\mytitle

### 2012-02-23 papers/SAS2012/implicitization.tex
Compactage

\renewcommand{\baselinestretch}{1}

@@

Because of the non-monotonicity of the results of abstract interpretation with widening operators, it is difficult to conclude that some abstraction is more precise than another based on theoretical local precision results. We thus conducted extensive comparisons between our new techniques and previous ones, on a variety of open-source packages. We also took the opportunity to compare the precision of various classical abstract domains (convex polyhedra, octagons, intervals).
\end{abstract}

@@

Widening operations have a somewhat counterintuitive behavior: the
result of an analysis (postcondition) is not necessarily monotonic
with respect to the precondition.
\avirer{
For instance, classical interval
analysis with widening and decreasing iterations on the loop
\lstinline|while (x != 10) x=x+1;| yields a loop invariant $x \in
[0,+\infty)$ if the precondition is $x \in [0,0]$, but $x \in [0,10]$
(strictly stronger) if the precondition is $x \in [0,10]$ (strictly
weaker).
}
This means that, when using widenings, being locally more precise \avirer{(for instance, by using more expressive abstract domains, or widening operators that climb more slowly \cite{BagnaraHRZ05SCP})} does not necessarily translate into higher final precision.
\avirer{
It is almost always possible to concoct examples where a supposedly more precise abstraction (e.g. polyhedra) yields less precise results than a less precise one (e.g. intervals), but are these examples representative of real programs?
}
This justifies our recourse to evaluation on real, large programs~(\S~\ref{sec:compare_techniques}).

@@

%\MM{Je trouve qu'il manque une vue de haut niveau quelque part par
%  ici. Dire qu'en gros, l'algo, c'est (en pseudo-code ou en langue naturelle) :
%
%Sans ca, enchainer tout de suite sur ``ascending iterations'' est un peu brutal.
%
%Ensuite, on peut rafiner la définition de ``Subset'' ($A$ et $P$), et
%enchainer sur l'algo 2.
%}

@@

The order of steps is important: narrowing has to be performed before
adding new paths, or spurious new paths would be added to $P$.
Starting with the addition of new paths avoids% wasting time
doing the ascending iterations on an empty graph.

>>>>

\renewcommand{\baselinestretch}{.97}

@@

Because of the non-monotonicity of the results of abstract interpretation with widening operators, it is difficult to conclude that some abstraction is more precise than another based on theoretical local precision results. We thus conducted extensive comparisons between our new techniques and previous ones, on a variety of open-source packages.
\end{abstract}

@@

\MM{J'avais insisté pour qu'on écrive un truc comme ça, mais si on ne
  met plus l'accent sur le côté expérimental, on peut sans doute
  supprimer ce paragraphe completement ?}
\avirer{
Widening operations have a somewhat counterintuitive behavior: the
result of an analysis (postcondition) is not necessarily monotonic
with respect to the precondition.
% For instance, classical interval
% analysis with widening and decreasing iterations on the loop
% \lstinline|while (x != 10) x=x+1;| yields a loop invariant $x \in
% [0,+\infty)$ if the precondition is $x \in [0,0]$, but $x \in [0,10]$
% (strictly stronger) if the precondition is $x \in [0,10]$ (strictly
% weaker).
This means that, when using widenings, being locally more precise \avirer{(for instance, by using more expressive abstract domains, or widening operators that climb more slowly \cite{BagnaraHRZ05SCP})} does not necessarily translate into higher final precision.
% It is almost always possible to concoct examples where a supposedly more precise abstraction (e.g. polyhedra) yields less precise results than a less precise one (e.g. intervals), but are these examples representative of real programs
This justifies our recourse to evaluation on real, large programs~(\S~\ref{sec:compare_techniques}).
}

@@

@@

The order of steps is important: narrowing has to be performed before
adding new paths, or spurious new paths would be added to $P$.
Starting with the addition of new paths avoids
doing the ascending iterations on an empty graph.
